Type Safe Redis Queries

### 2017-07-13 TyDe2017/main-tyde.tex
Lightweight revisions to reflect some of the reviewers' comment.
Auto stash before merge of "master" and "origin/master"

\documentclass[sigplan,10pt,review]{acmart}\settopmatter{printfolios=true}

\makeatletter\if@ACM@journal\makeatother
%% Journal information (used by PACMPL format)
%% Supplied to authors by publisher for camera-ready submission
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{1}
\acmArticle{1}
\acmYear{2017}
\acmMonth{1}
\acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}
\else\makeatother
%% Conference information (used by SIGPLAN proceedings format)
%% Supplied to authors by publisher for camera-ready submission
\acmConference[TyDe'17]{2nd Workshop on Type-Driven Development}{September 3, 2017}{Oxford, UK}
\acmYear{2017}
\acmISBN{978-x-xxxx-xxxx-x/YY/MM}
\acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}
\fi

\setcopyright{none}     
\bibliographystyle{ACM-Reference-Format}

@@

@@

\keywords{Haskell, Redis, Dependent Type, Type Safety, Key-Value Store}

>>>>

\documentclass[sigplan]{acmart}
\settopmatter{printfolios=true}

\makeatletter\if@ACM@journal\makeatother
%% Journal information (used by PACMPL format)
%% Supplied to authors by publisher for camera-ready submission
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{1}
\acmArticle{1}
\acmYear{2017}
\copyrightyear{2017}
\acmPrice{15.00}

\setcopyright{rightsretained}
\bibliographystyle{ACM-Reference-Format}

@@

\setlength{\mathindent}{10pt}

@@

\keywords{Haskell, Redis, Type-Level Programming Type Safety, Key-Value Store}
